On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-12-01 Manuscript/manuscript.tex
Laid Out Comments
Responded with Some Ideas

To summarize, the performance of the CIs depends on the target parameter. When
estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
perform noticeably better than the others. However, when estimating $\phi$, the 
choice of method is of utmost importance as to avoid coverage deterioration. A 
smaller sample size is generally required to estimate a parameter for a sample 
with a negative $\phi$ versus a positive $\phi$ of the same magnitude. In order 
to know if coverage will increase as the strength of the temporal dependence 
increases, one need to know what the parameter of interest is, and in the case 
of $\mu$, the direction of the serial dependence. The BC approach does not seem 
to be correcting bias appropriately when estimating $\phi$. Like the percentile 
method, the recentered percentile method uses the spread from the bootstrap to 
construct the width of the CI. However, the recentered approach, does not 
correct from the original point estimate $\hat\theta_n$.

>>>>

To summarize, the performance of the CIs depends on the target parameter. When
estimating $\mu$ and $\sigma_x$, any CI will do, although Student's $t$ CIs
perform noticeably better than the others. However, when estimating $\phi$, the 
choice of method is of utmost importance as to avoid coverage deterioration. 
Coverage rates are acceptable at smaller sample 
sizes when phi is positive versus when phi is negative. In
other words, a larger sample size is generally required to estimate a 
parameter for a sample with a negative $\phi$ versus a positive $\phi$ of the 
same magnitude. In order 
to know if coverage will increase as the strength of the temporal dependence 
increases, one need to know what the parameter of interest is, and in the case 
of $\mu$, the direction of the serial dependence. The BC approach does not seem 
to be correcting bias appropriately when estimating $\phi$. Like the percentile 
method, the recentered percentile method uses the spread from the bootstrap to 
construct the width of the CI. However, the recentered approach, does not 
correct from the original point estimate $\hat\theta_n$.

### 2023-12-01 Manuscript/reply.tex
Responded with Some Ideas

% \jy{Confirm that all the locations mentioned really contain the stated changes.}
% \tw{check and revise}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\bibliographystyle{chicago}
\bibliography{cjiot}

>>>>

@@

\mc{Not sure what they mean by "non-parametric" CIs, maybe the Percentile, BC,
and BCA, and Recentered CIs? In Figure 4, we showed that the autocorrelation in
the bootstrap samples is generally smaller than in the original sample. 
Percentile, BC, and BCA CIs perform better when the temporal dependence is low.
In these circumstances, "non-parametric" CIs would work better}

@@

\mc{Can we include the page number in the superscript somehow? Otherwise it does
not fit the journal's style.}

@@

\mc{The Efron book refers to such tables as "confidence intervals based on 
bootstrap 'tables'"}

@@

\mc{Maybe we can add this to future studies}

@@

\mc{It is a journal style choice}

@@

\mc{It is the Wald-type interval, should we just mention the undercoverage in
the design section of simulation and cite a source?}

@@

\mc{Because of the deterioration, we found it hard to fix the limits on the 
y-axis without making the other rows look bad}

@@

\mc{addressed}

@@

\citep{ratick2009175}

@@

\mc{For the higher positive autocorrelations, a very large sample size is
required. We could try it for more extreme negative autocorrelations.}

@@

\citep[p.160]{efron1993introduction}
\citep[p.188]{efron1993introduction}

@@

\bibliographystyle{chicago}
\bibliography{citations}
